A general Nullstellensatz for generalized spaces

### 2022-04-04 paper-qcoh.tex
to do
typo
Counterexample demonstrating the necessity of the fp condition

\newcommand{\xra}[1]{\xrightarrow{#1}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\bbb}{\mathfrak{b}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\B}{\mathcal{B}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\OO}{\mathbb{O}}
\newcommand{\ZZ}{\mathbb{Z}}
\renewcommand{\SS}{\mathbb{S}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\PSh}{PSh}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\length}{length}
\DeclareMathOperator{\List}{List}
\DeclareMathOperator{\id}{id}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\renewcommand{\_}{\mathpunct{.}\,}
\newcommand{\effective}{ef{}fective\xspace}
\newcommand{\?}{\,{:}\,}
\newcommand{\realizes}{\Vdash}
\newcommand{\notnot}{\emph{not~not}\xspace}
\usepackage{soul}\setul{0.3ex}{}
\let\oldul\ul
\renewcommand{\ul}[1]{\text{\oldul{$#1$}}}
\newcommand{\affl}{\ensuremath{{\ul{\AA}^1}}\xspace}
\newcommand{\speak}[1]{\ulcorner\text{\textnormal{#1}}\urcorner}
\newcommand{\brak}[1]{\llbracket #1 \rrbracket}
\newcommand{\Mod}[1]{{#1}\mathrm{\text{-}mod}}

@@

Hence it is useful to turn to geometric theories which refer to a given
mathematical object. For instance, given a ring~$A$, there is the theory of
local localizations of~$A$, and its classifying topos is known in algebraic
geometry as the little Zariski topos of~$A$, the topos of sheaves over the
spectrum of~$A$. If~$A$ is reduced, this topos validates the dual condition that any
noninvertible element is zero. This property has been used to give a short and
even constructive proof of Grothendieck's generic freeness lemma,
substantially improving on previously published
proofs~\cite{blechschmidt:generic-freeness}.

@@

Following the Kripke--Joyal translation of the claim, similar as in the proof
of Theorem~\ref{thm:quasicoherence}, it suffices to show that
applying the sheafification functor to the isomorphisms provided by
Lemma~\ref{lemma:fp-double-dual} (over arbitrary slices) results in
isomorphisms of the same form. This fact follows from the lemma (applied twice)
that computing the internal Hom to a sheaf commutes with sheafification and
from the observation that the construction~``free~$U_\TT$-module modulo
relations'' is geometric, hence in particular commutes with sheafification.
\end{proof}

@@

@@

>>>>

\newcommand{\xra}[1]{\xrightarrow{#1}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\bbb}{\mathfrak{b}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\B}{\mathcal{B}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\OO}{\mathbb{O}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\QQ}{\mathbb{Q}}
\renewcommand{\SS}{\mathbb{S}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\PSh}{PSh}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\length}{length}
\DeclareMathOperator{\List}{List}
\DeclareMathOperator{\id}{id}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\renewcommand{\_}{\mathpunct{.}\,}
\newcommand{\effective}{ef{}fective\xspace}
\newcommand{\?}{\,{:}\,}
\newcommand{\realizes}{\Vdash}
\newcommand{\notnot}{\emph{not~not}\xspace}
\usepackage{soul}\setul{0.3ex}{}
\let\oldul\ul
\renewcommand{\ul}[1]{\text{\oldul{$#1$}}}
\newcommand{\affl}{\ensuremath{{\ul{\AA}^1}}\xspace}
\newcommand{\speak}[1]{\ulcorner\text{\textnormal{#1}}\urcorner}
\newcommand{\brak}[1]{\llbracket #1 \rrbracket}
\newcommand{\Mod}[1]{{#1}\mathrm{\text{-}mod}}

@@

Hence it is useful to turn to geometric theories which refer to a given
mathematical object. For instance, given a ring~$A$, there is the theory of
local localizations of~$A$, and its classifying topos is known in algebraic
geometry as the little Zariski topos of~$A$, the topos of sheaves over the
spectrum of~$A$. If~$A$ is reduced, this topos validates the dual field condition that any
noninvertible element is zero. This property has been used to give a short and
even constructive proof of Grothendieck's generic freeness lemma,
substantially improving on previously published
proofs~\cite{blechschmidt:generic-freeness}.

@@

Following the Kripke--Joyal translation of the claim, similar as in the proof
of Theorem~\ref{thm:quasicoherence}, it suffices to show that
applying the sheafification functor to the isomorphisms provided by
Lemma~\ref{lemma:fp-double-dual} (over arbitrary slices) results in
isomorphisms of the same form. This fact follows from the fact that
the presheaf Hom into a sheaf is already a sheaf itself and
from the observation that the construction~``free~$U_\TT$-module modulo
relations'' is geometric, hence in particular commutes with sheafification.
\end{proof}

@@

\begin{rem}The finite presentability condition in
Lemma~\ref{lemma:fp-double-dual} cannot be dropped. For instance, in the case
that~$\TT$ is the theory of commutative rings with unit and~$A$ is the
ring~$\QQ$ of integers, we have~$\Spec(A^\sim) \cong \Spec(0^\sim)$, where~$0$
is the zero ring, as~$\QQ$ allows ring homomorphisms only in those finitely
presented rings in which~$1 = 0$ holds. Hence~$A^\sim$
and~$(U_\TT)^{\Spec(A^\sim)} \cong (U_\TT)^{\Spec(0^\sim)} \cong 0^\sim$ do not coincide.
\end{rem}

@@

% XXX Check: https://arxiv.org/abs/1811.08838
